Hierarchically Supervised Latent Dirichlet Allocation

### 2011-06-03 paper/experiments.tex
near submission fixes

As sensitivity and specificity can always be traded off, we examined
sensitivity for a range of values for two different parameters -- the prior
means for the regression coefficients and the threshold for the auxiliary
variables.  The goal in this analysis was to evaluate the performance of these
models subject to more or less stringent requirements for predicting positive
labels. These two parameters have important related functions in the model. The
prior mean in combination with the auxiliary variable threshold together encode
the strength of the prior belief that unobserved labels are likely to be
negative. Effectively, the prior mean applies negative pressure to the
predictions and the auxiliary variable threshold determines the cutoff. 
For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  This is a proper Bayesian
sensitivity analysis. In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference and the auxiliary variable threshold is varied
following inference.
%However, as intended, they both highlight model performance 
%under more or less stringent requirements for predicting positive labels.

Figure \ref{fig:main_results} shows the predictive performance of HSLDA 
relative to the three comparison models as a function of the prior mean
on regression coefficients as a receiver operating characteristic (ROC) curve. 
For low values of the auxiliary variable threshold, the models predict labels
in a more sensitive and less specific manner, creating the points in the upper
right corner of the ROC curve. As the auxiliary variable threshold is
increased, the models predict in a less sensitive and more specific manner,
creating the points in the lower left hand corner of the ROC curve. For all
values of the prior mean in both datasets HSLDA outperforms sLDA with
independent regressors. In the case of HSLDA with separately trained
regression, HSLDA outperforms in the clinical dataset but performs equally well
across the board with the retail product dataset.

>>>>

As sensitivity and specificity can always be traded off, we examined
sensitivity for a range of values for two different parameters -- the prior
means for the regression coefficients and the threshold for the auxiliary
variables.  The goal in this analysis was to evaluate the performance of these
models subject to more or less stringent requirements for predicting positive
labels. These two parameters have important related functions in the model. The
prior mean in combination with the auxiliary variable threshold together encode
the strength of the prior belief that unobserved labels are likely to be
negative. Effectively, the prior mean applies negative pressure to the
predictions and the auxiliary variable threshold determines the cutoff. 
For each model type, separate models were fit for each value of the 
prior mean of the regression coefficients.  This is a proper Bayesian
sensitivity analysis. In contrast, to evaluate
predictive performance as a function of the auxiliary variable threshold,
a single model was fit for each model type and prediction was evaluated
based on predictive samples drawn subject to different auxiliary variable
thresholds. These methods are significantly different since the prior mean
is varied prior to inference, and the auxiliary variable threshold is varied
following inference.
%However, as intended, they both highlight model performance 
%under more or less stringent requirements for predicting positive labels.

Figure \ref{fig:main_results} shows the predictive performance of HSLDA 
relative to the two comparison models as a function of the prior mean
on regression coefficients as a receiver operating characteristic (ROC) curve. 
For low values of the auxiliary variable threshold, the models predict labels
in a more sensitive and less specific manner, creating the points in the upper
right corner of the ROC curve. As the auxiliary variable threshold is
increased, the models predict in a less sensitive and more specific manner,
creating the points in the lower left hand corner of the ROC curve. For all
values of the prior mean in both datasets, HSLDA outperforms sLDA with
independent regressors. In the case of HSLDA with separately trained
regression, HSLDA outperforms in the clinical dataset but performs equally well
across the board with the retail product dataset.
